### 2011-05-13 paper/paper.tex

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle} which determines whether a given point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

@@

\bibitem{Vempala} Lov\'asz, L. and Vempala, S. Hit-and-Run from a corner. \emph{SIAM Journal on Computing}, 35(4):9851005, 2006.

>>>>

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. Sampling can also allow us to estimate the volume of a convex region (\cite{Dyer}, \cite{Vempala2}).

We phrase the problem as follows: we are given a convex region $\mathcal{R}$ in the form of a \emph{membership oracle} which determines whether a given point $x$ is in $\mathcal{R}$, along with a starting point $x_0$ in $\mathcal{R}$. The task is to sample a point from the region with with a distribution as close to uniform as possible.

@@

\bibitem{Vempala} Lov\'asz, L. and Vempala, S. ``Hit-and-Run from a corner." \emph{SIAM Journal on Computing}, 35(4):9851005, 2006.

\bibitem{Vempala2} Lov\'asz, L. and Vempala, S. ``Simulated Annealing in Convex Bodies and an $O^*(n^4)$ Volume Algorith." Journal of Computer and System Sciences, Vol. 72, Issue 2, March 2006.
